Kronos \& Krios: TBD

### 2017-05-04 paper/ms.tex
intro sketch ... first attempt

\author{
  Semyeong Oh\altaffilmark{\pu,\lead},
  APW, JMB, KH, NL, DWH, DNS
}

@@

Wide binaries are valuable tools for studying star and planet formation as well as
Galactic dynamics and chemical evolution.
They tidally disrupt.

% section introduction (end)

>>>>

\author{
  Semyeong Oh\altaffilmark{\pu,\lead},
  APW, JMB, KH, NL, DWH, DNS, JW
}

@@

Wide binaries are valuable tools for studying star and planet formation as well as
Galactic dynamics and chemical evolution.
In the context of studying the evolution of the Milky Way, they are useful for
two main reasons.
First, because wide binaries are weakly bound systems that may be tidally
disrupted by e.g., field stars, molecular clouds, or the Galactic tidal field,
their statistics can be informative of the Galactic mass distribution.
\todo{Give specific examples.}
On the other hand, they are also a prime target to test the
chemical tagging hypotheses that we may trace back a group of co-eval stars
by detailed chemical abundance patterns as ``tag''s.
A multiple-star system of any size that we believe are co-eval,
with massive open clusters at one extreme, can serve this purpose.
Wide binaries are at the other extreme in that we may be less confident of
their coevality but they are much more abundant than the larger systems like open clusters.

Independently, in efforts to connect the host star's chemistry to
its planetary system, wide binaries with similar or very different planetary systems around
component stars are very useful as chemical signatures related to planet formation or accretion
can be revealed in a differential sense without any regard to Galactic chemical evolution
as long as we assume that the two stars should have been born together with identical chemistry.
\todo{Give examples and summary: Teske, Mack, Melendez.}

So far the strongest evidence for accretion of planetary material by host star comes
from spectral analysis of polluted white dwarfs.
\todo{Discuss Zuckerman, Klein}.

Here, we report and discuss the discovery of a co-moving pair of solar twin stars,
HD~240429 and HD~240430, with unusual chemical abundance and differential abundance patterns
that strongly suggest a dramatic accretion of planetary material by the two stars.
\todo{section summary}
